What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-25 lda-paper.tex
minor touchups and     - [X] Fix the Last Diagram - more contrast?

\usepackage[usenames]{color}
\definecolor{changecolor1}{rgb}{0.5,0.3,0.08} 
\definecolor{changecolor2}{rgb}{0.3,0.08,0.45} 
\definecolor{changecolor3}{rgb}{0.3,0.45,0.45} 
\definecolor{changecolor4}{rgb}{0.0,0.3,0.0} 
\newcommand{\hl}[1]{{\color{changecolor1} #1 }}
\newcommand{\hla}[1]{{\color{changecolor2} #1 }}
\newcommand{\hlb}[1]{{\color{changecolor3} #1 }}
\newcommand{\hlc}[1]{{\color{changecolor4} #1 }}

@@

\newcommand{\affaddr}[1]{#1}
\newcommand{\aemail}[1]{#1}
%\numberofauthors{5}
\author{
%\alignauthor
Abram Hindle and Michael W. Godfrey and Richard C. Holt\\
%\affaddr{David Cheriton School of Computer Science}\\
\affaddr{University of Waterloo}\\
\affaddr{Waterloo, Ontario}\\
\affaddr{Canada}\\
\aemail{\{ahindle,migod,holt\}@uwaterloo.ca}
%\alignauthor
% \and
% Michael W. Godfrey\\
% %\affaddr{David Cheriton School of Computer Science}\\
% \affaddr{University of Waterloo}\\
% \affaddr{Waterloo, Ontario}\\
% \affaddr{Canada}\\
% \aemail{migod@cs.uwaterloo.ca}
% %\alignauthor
% \and
% Richard C. Holt\\
% %\affaddr{David Cheriton School of Computer Science}\\
% \affaddr{University of Waterloo}\\
% \affaddr{Waterloo, Ontario}\\
% \affaddr{Canada}\\
% ;\aemail{holt@cs.uwaterloo.ca}
%\alignauthor
%\and
%Gregorio Robles\\
%\affaddr{GSyc}\\
%\affaddr{Universidad Rey Juan Carlos}\\
%\affaddr{Madrid}\\
%\affaddr{Spain}\\
%\aemail{grex@gsyc.escet.urjc.es}
}

@@

\hla{ The questions that we wish to address deal with the past and
  topics development that occurred in the past.  What happened in
  the previous iteration of a project's development?  What were the
  developers working on? What was the developer in the next cubicle
  working on? Which common topics and issues were dealt with in the
  current release of the software? What were the topics of the
  previous release? Given the requirements agreed to at the start of
  the iteration did our developers work on them?  What else did they
  work on?  }

@@

The query optimizer was a topic that recurred during MaxDB's
development. In our plots, topics that mention \emph{optimizer} occur
four times, yet in the global-trend-view (Figure
\ref{fig:statictopics}, explained in Section \ref{ref:compare}) it is not in any of the topics. A query
optimizer is an important component of an DBMS, but as we have shown
it does not appear as a topic on its own. We tried to remove words to
see if we could get an \emph{optimizer} topic. After removing stop
words and then two of the most common words, the global analysis
\hla{
finally had a topic with optimizer in its topic ten words. Our
analysis shows that optimizer was important but it had been obscured
by the global topic analysis, which used the entire history of
messages, but would have been noticed using the more local topic
analysis such as our windowed topic analysis, which used a window of
messages.
}

>>>>

\usepackage[usenames]{color}
\definecolor{changecolor1}{rgb}{0.5,0.3,0.08} 
\definecolor{changecolor2}{rgb}{0.3,0.08,0.45} 
\definecolor{changecolor3}{rgb}{0.3,0.45,0.45} 
\definecolor{changecolor4}{rgb}{0.0,0.3,0.0} 
% \newcommand{\hl}[1]{{\color{changecolor1} #1 }}
% \newcommand{\hla}[1]{{\color{changecolor2} #1 }}
% \newcommand{\hlb}[1]{{\color{changecolor3} #1 }}
% \newcommand{\hlc}[1]{{\color{changecolor4} #1 }}

\newcommand{\hl}[1]{#1}
\newcommand{\hla}[1]{#1}
\newcommand{\hlb}[1]{#1}
\newcommand{\hlc}[1]{#1}

@@

\newcommand{\affaddr}[1]{#1}
\newcommand{\aemail}[1]{#1}
%\numberofauthors{5}
\author{
%\alignauthor
Abram Hindle, Michael W. Godfrey and Richard C. Holt\\
%\affaddr{David Cheriton School of Computer Science}\\
\affaddr{University of Waterloo}\\
\affaddr{Waterloo, Ontario}\\
\affaddr{Canada}\\
\aemail{\{ahindle,migod,holt\}@uwaterloo.ca}
%\alignauthor
% \and
% Michael W. Godfrey\\
% %\affaddr{David Cheriton School of Computer Science}\\
% \affaddr{University of Waterloo}\\
% \affaddr{Waterloo, Ontario}\\
% \affaddr{Canada}\\
% \aemail{migod@cs.uwaterloo.ca}
% %\alignauthor
% \and
% Richard C. Holt\\
% %\affaddr{David Cheriton School of Computer Science}\\
% \affaddr{University of Waterloo}\\
% \affaddr{Waterloo, Ontario}\\
% \affaddr{Canada}\\
% ;\aemail{holt@cs.uwaterloo.ca}
%\alignauthor
%\and
%Gregorio Robles\\
%\affaddr{GSyc}\\
%\affaddr{Universidad Rey Juan Carlos}\\
%\affaddr{Madrid}\\
%\affaddr{Spain}\\
%\aemail{grex@gsyc.escet.urjc.es}
}

@@

\hla{ The questions that we wish to address deal with the past and
  topics development that occurred in the past.  What happened in
  the previous iteration of a project's development?  What were the
  developers working on? What were the topics of the
  previous release? Given the requirements agreed to at the start of
  the iteration did our developers work on them?  What else did they
  work on?  }

@@

The query optimizer was a topic that recurred during MaxDB's
development. In our plots, topics that mention \emph{optimizer} occur
four times, yet in the global-trend-view (Figure
\ref{fig:statictopics}, explained in Section \ref{sec:compare}) it is not in any of the topics. A query
optimizer is an important component of an DBMS, but as we have shown
it does not appear as a topic on its own. We tried to remove words to
see if we could get an \emph{optimizer} topic. After removing stop
words and then two of the most common words, the global analysis
\hla{
finally had a topic with optimizer in its topic ten words. Our
analysis shows that optimizer was important but it had been obscured
by the global topic analysis, which used the entire history of
messages, but would have been noticed using the more local topic
analysis such as our windowed topic analysis, which used a window of
messages.
}
